Switch equivalence and weak prime domains for left-linear DPO rewriting systems

### 2024-11-22 full_version/fusione.tex
minori

\usepackage{pgf}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning}
\tikzstyle{node}=[circle, draw=black, minimum size=1mm]
\tikzstyle{trans}=[font=\scriptsize]
\tikzstyle{lab}=[font=\small]

@@

@@

\title{Switch equivalence and weak prime domains for fusions}
\author{Paolo Baldan\and Davide Castelnovo\and  Andrea Corradini\and Fabio Gadducci}

@@

\begin{document}
\maketitle

\tableofcontents

@@

 \include{leftlinear.tex}
\include{permutations.tex}

>>>>

\usepackage{pgf}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning,calc}
\tikzstyle{node}=[circle, draw=black, minimum size=1mm, inner sep=1.5pt, font=\tiny]

\tikzstyle{trans}=[font=\scriptsize]
\tikzstyle{lab}=[font=\small]
\tikzset{
	coloredge/.style={
		->,
		color=red
		%densely dotted
	}
}

\tikzset{
	colorloop/.style={
		loop,
		color=red
		%densely dotted
	}
}

\tikzcdset{
	perm/.style={
		shorten >=-1mm, shorten <=-1mm,
		-,
		% dotted
	}
}

@@

\newcommand{\gph}[1]{\textbf{\textup{{#1}-Graph}}}

@@

% direct shift
\newcommand{\shift}[1]{\ensuremath{\mathrel{{\leftrightsquigarrow}_{#1}}}}

\title{Switch equivalence and weak prime domains for left-linear DPO rewriting systems}
\author{Paolo Baldan\and Davide Castelnovo\and  Andrea Corradini\and Fabio Gadducci}

@@

\begin{document}
\maketitle
\tableofcontents

@@

\include{permutations.tex}
 \include{leftlinear.tex}
